---
title: "Why do swing states matter so much?(Or some other political title)"
author: "Jaffa Romain & Anees Shaikh"
abstract: "idk if this is super needed since he hasn't put it in the pdf"
date: 2020-10-01T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r,echo=FALSE, message=FALSE}
#Code chunks with all our imports
library(tidyverse)
library(skimr)
library(visdat)
```
# Non-Technical executive summary

A little bit about the purpose of this survey, and

# Introduction

This is the part where we should write why we're doing this. For the purpose of this survey, we'll be focusing on the riding of Richmond Hill in Ontario. This is a riding that can be categorized as a **swing riding**. Swing ridings are ridings that may change allegiances to parties between elections, or have hotly contested votes. They represent a keen focus of most political parties, as elections can come down to the wire, and swing ridings often make the difference. 

## Richmond Hill electory history
Richmond Hill has swung between Conservatives and Liberals  


# Survey methodology

In this part we can talk about how we've set our survey up. We should probably make references to the readings here(p.13 of Wu & Thompson reading).
Inlcude a link for people to see what questions we're asked. 

Things we should write down here:

- Population
- Frame
- sample
- sampling methods
- how we reached our desired respondents
- cost
- steps we took to deal with non-respondents and effects(we could show this via a graph too)


# Results




```{r,echo=FALSE, message=FALSE}
#code chunks for all our libraries
library(tidyverse)
library(skimr)
library(visdat)
```



```{r}
#Simulation of Q:  Whom did you vote for in the last elections?
list_of_parties <- c("Liberals", "Conservatives", "Green Party", "NDP", "People's", "Rhinoceros")

prob_of_voting <- c(0.44,0.42,0.03,0.08,0.01,0.002)


#graphing the simulation
sample(list_of_parties, 37000, replace = TRUE, prob = prob_of_voting) %>% 
  as_tibble() %>% 
  rename(party_2019 = value) %>% 
  ggplot(aes(x = party_2019, fill = party_2019)) + 
  geom_bar() + 
  scale_fill_manual(values = c("blue", "green", "red", "orange", "brown", "pink")) +
  labs(title = "Surveyor response to: Whom did you vote for in the 2019 federal elections?",
       subtitle = "The People's party and Rhinoceros party were new additions to this election.",
       x = "Federal Party",
       y = "Number of votes",
       fill = "Party",
       tag = "[1]")



```



```{r}
#Simulation of Q:  Whom did you vote for in the 2015 elections?
list_of_parties <- c("Liberals", "Conservatives", "Green Party", "NDP")

prob_of_voting <- c(0.46,0.43,0.03,0.08)

sum(prob_of_voting)

#graphing the simulation
sample(list_of_parties, 37000, replace = TRUE, prob = prob_of_voting) %>% 
  as_tibble() %>% 
  rename(party_2015 = value) %>% 
  ggplot(aes(x = party_2015, fill = party_2015)) + 
  geom_bar() + 
  scale_fill_manual(values = c("blue", "green", "red", "orange", "brown", "pink")) +
  labs(title = "Surveyor response to: Whom did you vote for in the 2015 federal elections?",
       x = "Federal Party",
       y = "Number of votes",
       fill = "Party",
       tag = "[2]")
```
```{r}
#Simulation of Q:  Overall, how would you rate the performance of the current federal government party(1-10)?
set.seed(1)


#graphing the simulation
rnorm(37000, mean = 7, sd  = 1) %>% 
  as_tibble() %>% 
  rename(rating = value) %>% 
  ggplot(aes(x = rating)) + 
  geom_histogram() +  
  labs(title = "How would you rate the performance of the current federal government party?",
       subtitle = "The rating was on a scale of 1-10",
       x = "Rating",
       y = "Number of responses",
       tag = "[3]")
```





```{r}
#Simulation of Q:  If you could vote tomorrow, which of the parties would you vote for?
list_of_parties <- c("Liberals", "Conservatives", "Green Party", "NDP","Other")

prob_of_voting <- c(0.446,0.444,0.025,0.08,0.005)

sum(prob_of_voting)

#graphing the simulation
sample(list_of_parties, 37000, replace = TRUE, prob = prob_of_voting) %>% 
  as_tibble() %>% 
  rename(party_2020 = value) %>% 
  ggplot(aes(x = party_2020, fill = party_2020)) + 
  geom_bar() + 
  scale_fill_manual(values = c("blue", "green", "red", "orange", "brown", "pink")) +
  labs(title = "If you could vote tomorrow, which of the parties would you vote for?",
       x = "Federal Party",
       y = "Number of votes",
       fill = "Party",
       tag = "[4]")
```



# Discussions


# Weaknesses and Biases


# Code appendix





```{r,echo=FALSE, message=FALSE}

citation("tidyverse")
```

