---
title: "Why do swing states matter so much?(Or some other political title)"
author: "Jaffa Romain & Anees Shaikh"
abstract: "idk if this is super needed since he hasn't put it in the pdf"
date: 2020-10-01T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r,echo=FALSE, message=FALSE}
#Code chunks with all our imports
library(tidyverse)
library(skimr)
library(visdat)
```
# Non-Technical executive summary

A little bit about the purpose of this survey, and

# Introduction

This is the part where we should write why we're doing this. Which riding/province we're focusing on and why them. 


# Survey methodology

In this part we can talk about how we've set our survey up. We should probably make references to the readings here(p.13 of Wu & Thompson reading).
Inlcude a link for people to see what questions we're asked. 

Things we should write down here:

- Population
- Frame
- sample
- sampling methods
- how we reached our desired respondents
- cost
- steps we took to deal with non-respondents and effects(we could show this via a graph too)


# Results

**We find that most people that make a lot of money...**

# Discussions


# Weaknesses and Biases


# Code appendix

```{r}
#Code to simulate data based on method of sampling we've chosen

#most likely going to have to use some form of 
  #set.seed
  #rnorm(2000, mean = x, sd = y)
```


```{r}
#EDA for our data
```



```{r,echo=FALSE, message=FALSE}
#code chunks for all our citations
library(tidyverse)
library(skimr)
library(visdat)
```

